Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-06-10 Paper/paper.tex
added s4 figs

\includegraphics[trim={3cm 0 0 0},width=2.\columnwidth]{plots/TTLambdaCIWidths90_0_Lambda_SNR.pdf}
%\includegraphics[trim={3cm 0 0 0},width=2.3\columnwidth]{plots/TTLambdaCIWidths90_0_Lambda_SNR.pdf}

>>>>

\includegraphics[width=1.8\columnwidth]{plots/SingleSystem_q4_0_mc2_25_chi0_50}
\caption{We show here the probability distribution recovered for the NS tidal
deformability parameter $\lambdans$ from a GW injection, with the following
parameters characterizing the binary:
$q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$, and
$\lambdans=2000$. The templates used here {\it ignore} tidal effects.
These figures show that this approximation holds up to (SNR)
$\rho\simeq 30-50$.
In each panel- the dashed red line marks the {\it measured} value of
$\lambdans$,
which is given by the median of its probability distribution.
The {\it true} value is marked by the dashed green line. The difference
between the true and measured values is the systematic bias introduced
by ignoring tidal effects in templates. The darker shading shows
the recovered $90\%$ confidence interval for $\lambdans$. The width of this
region is a direct measure of our statistical uncertainty.
Comparing systematic and statistical errors, we find that:
at $\rho=20$, $\lambdans$ measurement is dominated by statistical
errors; at $\rho=30$, the two become comparable; and 
for louder signals ($\rho\simeq50$), the systematic errors dominate.
\label{fig:SingleSystemLambdaPDFvsSNR}
% #################
\includegraphics[trim={3cm 0 0 0},width=1.9\columnwidth]{plots/TTLambdaRawCIWidths90_0_Lambda_SNR}
% \includegraphics[trim={3cm 0 0 0},width=2.\columnwidth]{plots/TTLambdaCIWidths90_0_Lambda_SNR.pdf}
